---
title: "Data 605 Homework Week-2"
output:
  html_document:
    css: ./lab.css
    highlight: pygments
    theme: cerulean
  pdf_document: default
---

##---------------------------------------------------------------------------
###**Student Name :** Sachid Deshmukh
###**Date :** 02/09/2019

* > [GitHub Location for rmd 
file](https://github.com/mlforsachid/MSDSQ2Data605/blob/master/Week2/HW-2/SachidVijay.Deshmukh60.Rmd)

* > [RPubs location of published file](http://rpubs.com/sachid/Data605Week2HW)

##---------------------------------------------------------------------------

#### Problem Set-1

* **Show that AT*A != A*AT n general. (Proof and demonstration.)**

If A is an mXn matrix where m = no of rows and n = no of columns and m != n then A*AT will be mXm matrix and AT*A will be  nxn matrix. since m !=n these two results can not be same


```{r}
tryCatch(
  {
A <- matrix(c(3,5,7,6,4,2), nrow=2, byrow=TRUE)
At <- t(A)

AAT = A %*% At
ATA = At %*% A


  AAT== ATA
  },error = function(e){(print (e))
})
```

* **For a special type of square matrix A, we get AT*A = A*AT Under what conditions could this be true?**

This can be true for a matrix where m = n and AT = A

```{r}
A <- matrix(c(4,5,3,5,4,3,3,3,8), nrow=3, byrow=TRUE)
At <- t(A)

AAT = A %*% At
ATA = At %*% A

print(AAT == ATA)

```

#### Problem Set-2

```{r}

MatrixDecomposition <- function(A) {
  
  U <- A
  n <- dim(A)[1]
  L <- diag(n)
  
  
  # For loops to construct LTM and UTM
  for(i in 2:n) {
    for(j in 1:(i-1)) {
      multiplier <- -U[i,j] / U[j,j]
      U[i, ] <- multiplier * U[j, ] + U[i, ]
      L[i,j] <- -multiplier
    }
  }
  return(list(L,U))
}

A <- matrix(c(5,8,-1,2,12,9,7,8,11), nrow=3, byrow=TRUE)
LU <- MatrixDecomposition(A)
L<-LU[[1]]  
U<-LU[[2]]

A == L %*% U

```
