---
title: "Data 605 Discussion Week-12"
output:
  html_document:
    css: ./lab.css
    highlight: pygments
    theme: cerulean
  pdf_document: default
---

##---------------------------------------------------------------------------
###**Student Name :** Sachid Deshmukh
###**Date :** 04/18/2019
* > [GitHub Location for rmd file](https://github.com/mlforsachid/MSDSQ2Data605/blob/master/Week12/Discussion/SachidVijay.Deshmukh60.Rmd)

* > [RPubs location of published file](http://rpubs.com/sachid/Data605Week12Disc)

##---------------------------------------------------------------------------

**In this example we will use built in cars dataset to build multiple regression model**

**Aim is to predict car mileage using car displacement, horsepower, drat and weight**


**1] Data Analysis **

```{r}
head(mtcars)
str(mtcars)
attach(mtcars)
```

**2] Build Model**

```{r}
model <- mpg~disp + hp + drat + wt
fit <- lm(model, mtcars)
fit

```

**3] Model Summary.**
```{r}
summary(fit)
```
 
 **From the model summary we can conclude that**
 
 **1. Horsepower and Weight are the strong predictor of mileage**
 
 **2. Displacement and drat are not helping in predicting car mileage**
 
 **3. Negative coefficient for horsepower and weight indicates that mileage increases as weight and horsepower decreases and vice versa**
 
**Residual Analysis**

```{r}
plot(fit$residuals)
```

**Residuals are y axis imbalance indicating some outliers in the data**

**Residuals show some non-linear pattern indicating relationship of mileage and predictor variables is not strictly linear**

```{r}
qqnorm(fit$residuals)
```

**Residuals are not normally distributed indicating weight and horsepower are not the only predictor for mileage. We need to add some more predictor for good fit of the model**
