---
title: "Data 605 Homework Week-5"
output:
  html_document:
    css: ./lab.css
    highlight: pygments
    theme: cerulean
  pdf_document: default
---

##---------------------------------------------------------------------------
###**Student Name :** Sachid Deshmukh
###**Date :** 02/27/2019

* > [GitHub Location for rmd 
file](https://github.com/mlforsachid/MSDSQ2Data605/blob/master/Week4/HW-4/SachidVijay.Deshmukh60.Rmd)

* > [RPubs location of published file](http://rpubs.com/sachid/Data605Week5HW)

##---------------------------------------------------------------------------

### Choose independently two numbers B and C at random from the interval [0, 1] with uniform density. Prove that B and C are proper probability distributions.Note that the point (B,C) is then chosen at random in the unit square.

**Let's simulate B and C using uniform distribution function**

```{r}
# Take sample of 1000 random numbers from uniform distribution with min = 0 and max =1

B = runif(1000, min=0, max=1 )
C = runif(1000, min=0, max=1 )
```

**1. Find the probability that B+C < 0.5 **

```{r}
result = B + C
print(length(result[result < 0.5])/length(result))
```

**2. Find the probability that BXC < 0.5 **

```{r}
result = B * C
print(length(result[result < 0.5])/length(result))
```

**3. Find the probability that ABS(B-C) < 0.5 **

```{r}
result = abs(B - C)
print(length(result[result < 0.5])/length(result))
```

**4. Find the probability that MAX(B, C) < 0.5 **

```{r}
result = pmax(B, C)
print(length(result[result < 0.5])/length(result))
```

**5. Find the probability that MIN(B, C) < 0.5 **

```{r}
result = pmin(B, C)
print(length(result[result < 0.5])/length(result))
```
