---
title: "Data 605 Homework Week-4"
output:
  html_document:
    css: ./lab.css
    highlight: pygments
    theme: cerulean
  pdf_document: default
---

##---------------------------------------------------------------------------
###**Student Name :** Sachid Deshmukh
###**Date :** 02/24/2019

* > [GitHub Location for rmd 
file](https://github.com/mlforsachid/MSDSQ2Data605/blob/master/Week4/HW-4/SachidVijay.Deshmukh60.Rmd)

* > [RPubs location of published file](http://rpubs.com/sachid/Data605Week4HW)

##---------------------------------------------------------------------------

### Problem set 1

**1. Matrix A = **

```{r}
A <- matrix(c(1,-1,2,0,3,4), nrow=2)
print(A)
```

**2. Matrix X = **

```{r}
X <- A %*% t(A)
print(X)
```

**3. Matrix Y = **

```{r}
Y <-   t(A) %*% A
print(Y)
```


**4. Sungular Value Decomposition of A**

```{r}
eigenX <- eigen(X)
eigenY <- eigen(Y)
svdA <- svd(A)
print(svdA)
```

**5. Validate that U is same as Eigen Vector of X **

```{r}
eigenX$vectors[,1] <- eigenX$vectors[,1] * (-1)
round(eigenX$vectors, digits=10) == round(svdA$u, digits=10)
```

**6. Validate that V is same as Eigen Vector of Y **

```{r}
eigenY$vectors[,1] <- eigenY$vectors[,1] * (-1)
round(eigenY$vectors[,1:2], digits=10) == round(svdA$v, digits=10)
```

**7. Validate that sigma is same as Square Root of Eigen Values of X **

```{r}
round(eigenX$values, digits=10) == round(svdA$d^2, digits=10)
```

### Problem set 2

**1. myinverse function definition**

```{r}
myinverse <- function(X) {
  
  # Get Matrix Dimension
  n <- dim(X)[1]
  
  # Matrix Inversion Loop
  Y <- matrix(0, n, n)
  for(i in 1:n) {
    for(j in 1:n) {
      Y[i,j] <- (-1)^(i+j)*det(matrix(X[-i,-j], n-1))
    }
  }
  
  # Calculate Inverse
  Z <- t(Y)/det(X)
  
  return(Z)
}
```

**2. Test myinverse function**

```{r}
A <- matrix(c(5,3,7,2,8,9,3,5,7), nrow=3)
print(A)

B <- myinverse(A)
print(B)
```

**3. Validate that A.B = Identity Matrix**

```{r}
I = round(A %*% B, digits=10)
print(I)
```