---
title: "Data 605 Homework Week-10"
output:
  html_document:
    css: ./lab.css
    highlight: pygments
    theme: cerulean
  pdf_document: default
---

##---------------------------------------------------------------------------
###**Student Name :** Sachid Deshmukh
###**Date :** 04/02/2019

* > [GitHub Location for rmd 
file](https://github.com/mlforsachid/MSDSQ2Data605/blob/master/Week10/HW-10/SachidVijay.Deshmukh60.Rmd)

* > [RPubs location of published file](http://rpubs.com/sachid/Data605Week10HW)

##---------------------------------------------------------------------------

**Smith is in jail and has 1 dollar; he can get out on bail if he has 8 dollars. A guard agrees to make a series of bets with him. If Smith bets A dollars, he wins A dollars with probability .4 and loses A dollars with probability .6. Find the probability that he wins 8 dollars before losing all of his money if**

**(a) he bets 1 dollar each time (timid strategy).**

```{r}
print((1.5^1-1)/(1.5^8-1))

```
**(b) he bets, each time, as much as possible but not more than necessary to bring his fortune up to 8 dollars (bold strategy).**

```{r}
print(dbinom(3,3,0.4))

```

**(c) Which strategy gives Smith the better chance of getting out of jail?**

Bold strategy with probability of 0.064 gives Smith better chance if getting out of jail
